\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Super Light Clients for ETH2}
\author{Shresth Agrawal\inst{1} \\ {\small Advisor: Dionysis Zindros\inst{2} \and Sören Petrat\inst{1}}}
%
\institute{Jacobs University Bremen \and Stanford University}
%
\maketitle
%
\begin{abstract}
Currently all of the self custody Ethereum wallets that run on browser or smart phone rely on single RPC full-node to get the state of the blockchain. These full-nodes can behave maliciously or get hacked. Due to the limitation of storage and bandwidth, running full-nodes or even light clients is not possible on such wallets. There already exists constructions for verifying Proof of Stake is sub-linear complexity. These constructions use interactive bisection games between the nodes to quickly sync with the latest state of the network. In this paper we propose a similar constructions specifically tailored for ETH2. 
\end{abstract}
%
%
%
\section{Introduction}
Goals and Settings

\section{Background}

\subsection{Blockchain}
\begin{description}
\item What are blockchains and why are they special 
\item Introduction of Bitcoin and Proof of Work
\end{description}

\subsection{ETH}
\begin{description}
\item Current Ethereum, its high adoptions
\item Centralization of Ethereum wallets
\item Transition to ETH2 PoS
\end{description}

\subsection{Proof of Stake}
Overview of components of proof of stake systems.

\subsection{ETH2}
ETH2 is the upcomming version of ETH1 which uses PoS. ETH2 merges two consensus protocols.
\subsubsection{Time}
Blocks, Epochs, etc
\subsubsection{Casper FFG}
Used for Finality. \cite{CasperFFG}

\subsubsection{LMD GHOST}
Secure only under good network conditions. \cite{Gasper}

\subsection{PoPoS}
Smartly uses bisection games to fast sync \cite{PoPos}

\subsubsection{Bisection Game}
Interactive games using Merkle Trees

\section{Construction}
Build PoPoS on ETH2 

\section{Experiments}
\section{Conclusion}
\subsection{Future Work}

\bibliographystyle{splncs04}
\bibliography{refs}
\end{document}
